DATA 624 Homework 5

### 2020-03-05 DATA624/HW5.Rmd
More work on HW5

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
```

@@

@@

@@

@@

@@

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
options(scipen=999)
```

@@

```{r}
ses_pigs <- ses(pigs, h = 4)
summary(ses_pigs)
```

**The `ses` function generates and $\alpha$ of `r ses_pigs$model$par[1]` and a $\iota_0$ of `r ses_pigs$model$par[2]`.**

@@

```{r}
# Get the first forecast
y_hat <- ses_pigs$mean[1]
# Get the standard deviation of the residuals
s <- sd(ses_pigs$residuals)
lower_ci <- y_hat - 1.96 * s
upper_ci <- y_hat + 1.96 * s
```

**The 95% CI is from `r round(lower_ci, 0)` to `r round(upper_ci, 0)`,**

@@

**The 95% CI produced by R is `r round(78611.97, 0)` to `r round(119020.8, 0 )`.R's CI is slightly wider than the CI we computed.**

@@

```{r}
autoplot(books) + 
  ggtitle("Daily Sale of Books")
```

**The series has an upwards trend.  There is only 30 days of data so I can't really speak to an seasonality or weekly effects with much confidence.  The paperback sales lagging hardback, or hardback and paperback being counter cyclical, but I would stress it's really too soon to make these claims.**

@@

```{r}
ses_paperback <- ses(books[, 1], h = 4)
autoplot(ses_paperback) +
  ylab("Paperback Book Sales")
```

```{r}
ses_hardback <- ses(books[, 2], h = 4)
autoplot(ses_hardback) +
  ylab("Hardback Book Sales")
```

@@

```{r}
accuracy(ses_paperback)
```

```{r}
accuracy(ses_hardback)
```

**The RMSE for the paperback model is 33.6 and 31.9 for the hardback model.**
